Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-05-29 analysis/paper/asymsam.Rmd
Arregla caption de figura metodos

```{r method, fig.cap = "(ref:method-cap", fig.width=6, fig.height=2.7, fig.env="figure*"}
sam_sep <- SAM[, eof[[1]]$right, by = .(lev)] %>% 
  setnames("hgt", "full") %>% 
  .[, c("sym", "asym") := list(mean(full), Anomaly(full)), by = .(lat, lev)]

>>>>

```{r method, fig.cap = "(ref:method-cap)", fig.width=6, fig.height=2.7, fig.env="figure*"}
sam_sep <- SAM[, eof[[1]]$right, by = .(lev)] %>% 
  setnames("hgt", "full") %>% 
  .[, c("sym", "asym") := list(mean(full), Anomaly(full)), by = .(lat, lev)]
